A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-04-22 paper.tex
edited remark

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Gm}{\mathbb{G}_m}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\newcommand{\Sect}{\mathrm{Sect}}
\renewcommand{\U}{\mathrm{U}}

\newcommand{\ham}{/\!\!/}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

@@

\begin{rmk}
There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ is such that the twisting supercharge $Q$ is of weight $+1$. 
One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. 
This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be purely even in the new $\ZZ/2$-degree.
\end{rmk}

>>>>

@@

\begin{remark}
There is a slight generalization of this regrading procedure where one only relaces the requirement that the $\alpha$-weight coincides mod 2 with the fermionic grading, only requiring that the twisting supercharge $Q$ is of weight $+1$.  Given an action $\alpha$ of this more general class, one can define a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously shifting the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be concentrated purely in the even $\ZZ/2$-degree part.
\end{remark}
